Appendix A: Deep Reinforcement Learning

### 2021-05-29 appendices/appendix-A-definitions.Rmd
Small edits

There is a multitude of exploration algorithms that we have not touched on, so it is important to say that the algorithms mentionned above are generally suited for dense reward or "easy-exploration" problems.
For "hard-exploration" problems -- for instance, environments that have very few state-action pairs with significant rewards, like a maze, are seen as hard-exploration problems --, more intricate and bespoke exploration algorithms tend to outperform.
We will not go over these algorithms for the sake of brevity but a good example of an algorithm for hard-exploration problems is @go-explore.

>>>>

There is a multitude of exploration algorithms that we have not touched on, so it is important to say that the algorithms mentioned above are generally suited for dense reward or "easy-exploration" problems.
For "hard-exploration" problems -- for instance, environments that have very few state-action pairs with significant rewards, like a maze, are seen as hard-exploration problems --, more intricate and bespoke exploration algorithms tend to outperform.
We will not go over these more advanced exploration algorithms but a good example is seen in @go-explore.
